Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-16 grove-paper.tex
Tweaks to paper

Finally, holes are represented by the absence of a child.
For example, in \autoref{fig:A simple tree with a hole-b} the absence of a right edge coming from \vSimpleTimes{}
corresponds to the hole on the right of the~\texttt{*} in~\texttt{x * \hole}.

@@

For example, in \autoref{fig:Move} Alice continues by
repositioning \texttt{\hole{} * y} from the left child of \texttt{+} to its right child.
This corresponds to the following sequence of graph edits, shown in \autoref{fig:Move}:
(a) delete \eWrapTimesWrapC{} leaving \vSimpleTimes{} temporarily orphaned and
(b) add \eMoveTimes{} to \vSimpleTimes{} in the right child position of \vWrapPlus{}.

>>>>

Finally, holes are represented by the absence of a child.
For example, in \autoref{fig:A simple tree with a hole-b} the absence of an \texttt{R} edge coming from \vSimpleTimes{}
corresponds to the hole on the right of the~\texttt{*} in~\texttt{x * \hole}.

@@

For example, in \autoref{fig:Move} Alice continues by
repositioning \texttt{\hole{} * y} from the left child of \texttt{+} to its right child.
This corresponds to the following sequence of graph edits, shown in \autoref{fig:Move}:
(a) delete \eWrapTimes{} leaving \vSimpleTimes{} temporarily orphaned and
(b) add \eMoveTimes{} to \vSimpleTimes{} in the right child position of \vWrapPlus{}.
